---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(CryptoShiny)
```


### Dataset_daily_hourly

```{r}
example1 <- day_hour("day", "01/12/2017", "01/08/2018", "BTC", "USD")
head(example1)
```

###lastweek minute data


```{r}

minuteExample <- lastweek_minute("BTC", "USD")
head(minuteExample)

```

###Tsp_data

```{r}
now <- round(as.numeric(as.POSIXct(Sys.time(), format="%Y/%m/%d")))
Tsp_data(now) %>% head()
```


###lastweek_news_counter example

```{r}
lastweek_news_counter("BTC") %>% head()
```



### Transfer daily or hourily data to weekly or monthly data


```{r}
example2 <- weekly_monthly_transformation(example1, "week")
head(example2)
```


```{r}
averages(example2, 5, 26, 12, 9)
```


### Master function (only works for non-minute data)

```{r}
example3 <- crypto("week", "01/12/2017", "01/08/2018", "BTC", "USD",5, 26, 12, 9)
tail(example3)
```

```{r}
example4 <- crypto("hour", "01/07/2018", "01/08/2018", "BTC", "USD",5, 26, 12, 9)
tail(example4)
```

### Function to get the correlation

```{r}
correlation <- crypto_correlation("01/09/2018", "01/10/2018", "GBP", "UBT")
print(correlation)
```

###Candlestick plot example

```{r}
candle_plot(data= example4, volume)
```

### Function to get the last Price from Multiple Platforms
```{r}
lastPrice <- getLastPriceMultiplePlatforms("BTC")
head(lastPrice)
```
### Function to get the last Price from Bitfinex
```{r}
lastPrice <- getLastPriceBitfinex("ETH", "BTC")
print(lastPrice)
```


### Function to get the Net Value in USD in pocket
```{r}
pocket <- c("USD" = 100000, "BTC" = 0, "ETH" = 0)
NetUSDValue(pocket, day = "11/12/2018")
```

### Function to do the transaction
```{r}
startday <- "01/10/2018"
pocket_log <- data.frame("date" = as.POSIXct(startday,format="%d/%m/%Y", origin = "1970-01-01",tz = "GMT"),
                         "NetUSDvalue" = 1000,"USD" = 1000,"EUR" = 0, "GBP" = 0, "BTC" = 0, "ETH" = 0, "BNB" = 0, "BCC" = 0, "NEO" = 0, "LTC" = 0, "QTUM" = 0, "ADA" = 0, "XRP" = 0, "EOS" = 0, "TUSD" = 0, "IOTA" = 0, "XLM" = 0, "ONT" = 0, "TRX" = 0, "ETC" = 0, "ICX" = 0, "VEN" = 0, "NULS" = 0, "VET" = 0, "PAX" = 0)
pocket_log <- transaction(pocket = pocket_log, unit = 0.02, buycurrency = "BTC", sellcurrency = "USD", day = "05/12/2018")
pocket_log <- transaction(pocket = pocket_log, unit = 0.002, buycurrency = "BNB", sellcurrency = "USD", day = "07/12/2018")
pocket_log <- transaction(pocket = pocket_log, unit = 100, buycurrency = "EUR", sellcurrency = "USD", day = "10/12/2018")
pocket_log
```


